Chemical tagging: \\ Identification of stellar phase-space structures \\ purely by chemical-abundance similarity

### 2016-01-13 papers/clusters.tex
notes
outline

DWH: Scaling of the data
DWH: number of clusters
DWH: restarts for local minima

@@

@@

>>>>

DWH: Scaling of the data
DWH: number of clusters
DWH: restarts for local minima
DWH: Citation out to numpy and sklearn.

@@

DWH: Visualize densest clusters.  Some of them are known clusters.
Show examples.

DWH: Do we have streams or other structures?

DWH: What have we demonstrated?

@@

DWH: grants and grant numbers.

DWH: SDSS-III and SDSS-IV.

DWH: NASA ADS
